---
title: "Activity 6 - Logistic Regression"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidymodels)
library(tidyverse)


```


```{r read in data}

resume <- read_csv("https://www.openintro.org/data/csv/resume.csv")


```


1. Is this an observational study or an experiment? Explain.

**Answer:** This is an observational study. Yes, they used random assignment but there is no control condition (real resumes belonging to real people). Random assignment != experiment.

2. The variable of interest is received_callback. What type of variable is this? What do the values represent?

**Answer:** `received_callback` is a categorical variable with two levels: yes and no.

3. For received_callback, create an appropriate data visualization using {ggplot2}. Be sure to provide more descriptive labels (both axes labels and value labels - there are many ways to do this) as well as an appropriate title.



```{r}

resume$received_callback <- as.factor(resume$received_callback)

# new = old
resume <- resume %>% 
  mutate(received_callback = fct_recode(received_callback,
                                        "No" = "0",
                                        "Yes" = "1"))
  

```


```{r custom palette}

cp <- c("deepskyblue4", "dimgrey")

```



```{r}



ggplot(data = resume) +
  geom_bar(aes(x = received_callback, fill = received_callback)) +
  scale_fill_manual(values = cp) +
  labs(title = "Applicant Callback Count", x = "Did Applicant Receive A Callback?", y = "Count")



```

4. Below, I provide you with a numerical summary table that should reiterate (i.e., provides numerical values) your plot in (3). Write the code to produce this table.

```{r}

resume %>% 
  group_by(received_callback) %>% 
  summarise(n = n()) %>% 
  mutate(percent = round(n/sum(n)*100, 2))


```

5. Using the output from (4) and (5), what do you notice?

**Answer:** Looking at the table we can see that over 90% of applicants did not receive a callback.

6. What is the probability that a randomly selected résumé/person will be called back?

$Pr({received\_callback} = Yes) = 0.08$

7. What are the odds that a randomly selected résumé/person will be called back?

$\frac{Pr(Y_i = Yes)}{Pr(Y_i = No)} = \frac{p_i}{1-p_i} = \frac{0.08}{1 - 0.08} = 0.08696$

The odds are 0.08696 to 1.

NOTE: THE NUMBERING IN THE DAY01 INSTRUCTIONS IS OFF. 6 AND 7 ARE REAPEATED 2X.

8. What is the probability that a randomly selected résumé/person perceived as Black will be called back?

$Pr({received\_callback} = Yes | Black) = 0.064$

9. What are the odds that a randomly selected résumé/person perceived as Black will be called back?




```{r}


resume_mod <- logistic_reg() %>%
  set_engine("glm") %>%
  fit(received_callback ~ race, data = resume, family = "binomial")

tidy(resume_mod) %>% 
  knitr::kable(digits = 3)


```


8. Write the estimated regression equation. Round to 3 digits


$\log\left(\frac{0.08}{1 - 0.08}\right) = -2.675 + 0.438$


9. Using your equation in (8), write the simplified estimated regression equation corresponding to résumés/persons perceived as Black. Round to 3 digits.


$\log\left(\frac{0.08}{1 - 0.08}\right) = -2.675 + 0.438(6.45)$


Based on your model, if a randomly selected résumé/person perceived as Black,

10. What are the log-odds that they will be called back?

11. What are the odds that they will be called back? How does this related back to your answer from (7)? Hint: In (9) you obtained the log-odds (i.e., the natural log-odds). How can you back-transform this value to obtain the odds?

12. What is the probability that will be called back? How does this related back to your answer from (6)? Hint Use the odds to calculate this value.

























